---
title: "SC20054 - Transcriptomic signatures of iPSC-derived dopamine neurons"
author: "Stephanie Strohbuecker"
subtitle: Integrating across all samples using the reference-based approach
output:
  html_document:
    df_print: paged
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      eval.after = "fig.cap",
                      fig.width = 12)
```

The following integrates the samples using the untreated sample as a reference. The approach is described [here](https://satijalab.org/seurat/v3.1/integration.html

```{r}
RMD_file_name <- "1-1.Integrate_samples_after_filtering_cluster"
```


## Libraries

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(here)

library(ggpubr)

library(Seurat)
```

## File locations
Specify the location of input and output
```{r}
# File path to the individual Seurat object list (pre-processed to remove low quality cells, label suspected doublets)
seurat_list <-
  readRDS(
    here(
      "output",
      "0-4.label_suspected_doublets",
      "Seurat_individual_sample_pre-processed_doublets_labelled.rds"
    )
  )

# Marker gene list provided
marker_gene_list <-
  openxlsx::read.xlsx(here(
    "input_data",
    "Midbrain_dopaminergic_neurons_marker_genes.xlsx"
  ),
  sheet = 2) %>%
  mutate(symbol = str_to_upper(symbol) %>% 
           str_trim()) %>% 
  group_by(cell_type) %>%
  group_split() %>%
  set_names(map(
    .,
    ~ .x$cell_type %>% unique() %>% 
      str_replace_all(" ", "_") %>% 
      str_replace_all("/", "_")
  ))

# Path to output and figures directories
output <- str_c(here(), "output", RMD_file_name, sep = "/")

if (!dir.exists(output)) {
  dir.create(output, recursive = TRUE)
}

figures_out <- str_c(here(), "figures", RMD_file_name, sep = "/")

if (!dir.exists(figures_out)) {
  dir.create(figures_out, recursive = TRUE)
}
```

While we removed suspected low quality cells previously, we did not filter out cells that are suspected doublets. Nonetheless, we labelled the suspected doublets both by setting a cut-off of more than 7000 detected features and also by identifying the suspected doublets with DoubletFinder.
```{r fig.height=12, fig.width=18, message=FALSE, warning=FALSE}
purrr::imap(seurat_list, function(Seur_obj, Seur_name) {
  sub_text <- Seur_obj@project.name %>%
    str_replace("_|\\.", " ") 
  
  ggarrange(
 DimPlot(Seur_obj, label = TRUE, group.by = "doublet_cutoff_7000") +
      NoLegend() +
      labs(subtitle = "Doublets identified with cut-off\nnumber of features > 7000") +
      coord_fixed(ratio = 1) +
      scale_x_discrete(breaks = NULL) +
      scale_y_discrete(breaks = NULL),
    
    DimPlot(Seur_obj, label = TRUE, group.by = colnames(Seur_obj[[]])[str_detect(colnames(Seur_obj[[]]), "^DF")]) +
      NoLegend() +
      labs(subtitle = "Doublets identified with DoubletFinder") +
      coord_fixed(ratio = 1) +
      scale_x_discrete(breaks = NULL) +
      scale_y_discrete(breaks = NULL),
    
    DimPlot(Seur_obj, label = TRUE, group.by = "RNA_snn_res.1") +
      NoLegend() +
      labs(subtitle = "Cluster with a resolution of 1") +
      coord_fixed(ratio = 1) +
      scale_x_discrete(breaks = NULL) +
      scale_y_discrete(breaks = NULL),
    
    DimPlot(Seur_obj, reduction = "umap", group.by = "Phase") +
      labs(subtitle = "Cell Cycle Phase") +
      scale_colour_discrete(name = "Cell cycle\nphase") +
      coord_fixed(ratio = 1) +
      scale_x_discrete(breaks = NULL) +
      scale_y_discrete(breaks = NULL),
    
    align = "hv",
    nrow = 1,
    ncol = 4
  ) %>%
    annotate_figure(top = text_grob(sub_text,
                                    face = "bold",
                                    size = 12))
  
}) %>%
  ggarrange(
    plotlist = .,
    nrow = length(seurat_list),
    ncol = 1,
    align = "hv"
  ) %>%
  annotate_figure(
    top = text_grob(
      "Labelling suspected doublets",
      face = "bold",
      size = 16
    )
  )
```

We are using the "standard " workflow to integrate the datasets
```{r normalize-variable-features, eval=TRUE, include=TRUE}
# Normalize and find variable features in each of the individual datasets
seurat_list <-
  map(seurat_list, function(Seur_obj) {
    NormalizeData(Seur_obj)
  })
seurat_list <-
  map(seurat_list, function(Seur_obj) {
    FindVariableFeatures(Seur_obj,
                         selection.method = "vst",
                         nfeatures = 2000)
  })
```

```{r}
# reference_dataset <- meta_data %>%
#   filter(condition == "0h_none") %>%
#   pull(sample_id)
```

Integrate the data using the anchors identified in the previous step. For the subsequent regression of the effect of the cell cycle set the `features.to.integrate` to all features, i.e. not just the variable ones as described [here](https://github.com/satijalab/seurat/issues/1500).

Note that we ran the integration procedure twice, once with using a reference dataset and once without. We will subsequently compare the two integration procedures. (Note furthermore that only when using  the reference-dataset-based integration did we integrate across all features).
```{r anchor-identification, eval=TRUE, include=TRUE}
# Identify anchors for subsequent data integration, the dimensionality of the dataset is set to 30 by default but may be varied over a broad range, e.g. between 10 and 50
anchors <-
  FindIntegrationAnchors(
    object.list = seurat_list,
    dims = 1:50,
    normalization.method = "LogNormalize"
    # reference = which(names(seurat_list) == reference_dataset)
  )
```

```{r}
saveRDS(anchors,
        file = str_c(output, "anchorset_for_integration.rds", sep = "/"))
```

```{r}
feat_to_int <-
  map(seurat_list, ~ rownames(.x)) %>% reduce(intersect)

data_integrated <-
  IntegrateData(
    anchorset = anchors,
    dims = 1:50,
    features.to.integrate = feat_to_int
  )

data_integrated

```

```{r, eval=TRUE, include=TRUE}
saveRDS(
  data_integrated,
  file = str_c(
    output,
    "seurat_list_filtered_integrated.rds",
    sep = "/"
  )
)
```