---
title: "SC20054 - Transcriptomic signatures of iPSC-derived dopamine neurons"
author: "Stephanie Strohbuecker"
subtitle: RNA velocity estimation with scVelo - quantification with Alevin (Salmon)
output:
  html_document:
    df_print: paged
---

The scVelo environment contains R4.0.3 as some of the packages required in R are only available with the most recent Bioconductor release. (use the following conda environment: `scvelo-0.2.2`)
```{bash, eval=False}
module purge
module load Anaconda3/2020.02
conda activate scvelo-0.2.2

cd .

R
```

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,
                      eval.after = "fig.cap",
                      fig.width = 12)
```


```{r}
RMD_file_name <- "3-1.RNA_velocity_quantification_with_Alevin"
```

In the following we follow the tutorial for [Alevin Velocity](https://combine-lab.github.io/alevin-tutorial/2020/alevin-velocity/):

# Libraries
```{r}
library(tidyverse)
library(here)
```

The fastq files are associated with the following sequencing runs:

All the folders can be accessed through:
`~/primary_data/`

Get the location of the fastq files
```{r}
file_information <- read_csv("./input/SC20054_design.csv") %>% 
  select_if(~any(!is.na(.))) %>% 
  filter(!is.na(fastq_1)) %>%
    mutate(
      fastq_id = str_remove_all(fastq_1, "^/.*ments/fastq/") %>%
        str_replace("/fastq/SC20054/", "_") %>%
        str_replace("_R\\d_", "_")) %>% 
  group_by(sample_lims) %>% 
  group_split() %>% 
  set_names(map(., ~ .x$sample_lims %>% unique()))
```


After the generation of the index, exonic and intronic abundances are quantified with [Alevin](https://salmon.readthedocs.io/en/latest/alevin.html).

```{bash, eval=FALSE}
almon alevin -l ISR -i Mus_musculus.GRCm38.89.expanded \
-1 AdultMouseRep3_S1_L001_R1_001.fastq.gz \
-2 AdultMouseRep3_S1_L001_R2_001.fastq.gz \
-o alevin_out -p 32 --tgMap Mus_musculus.GRCm38.89.annotation.expanded.tx2gene.tsv \
--chromiumV3 --dumpFeatures
```

```{r}
imap(file_information, function(sampl, sampl_nam) {
  read1_info <- str_c(sampl$fastq_1, collapse = " ")
  read2_info <- str_c(sampl$fastq_2, collapse = " ")
  organism <- unique(sampl$species) %>%  str_replace(" ", "_")
  slurm_cmd <-
    str_c(
      "sbatch -c 32 --time=24:00:00  --output=./alevin_quantification/",
      sampl_nam,
      ".log ./scripts/Run_alevin_quantification.sh '",
      read1_info,
      "' '",
      read2_info,
      "' ",
      sampl_nam,
      " '",
      organism,
      "'",
      sep = ""
    )
  system(slurm_cmd)
  slurm_cmd
})
```










